Acoustic Scene Classification: \\ Supervised and Unsupervised Approaches using the Scattering Transform

### 2016-06-21 paper/structureScene.tex
missing \fi to compile
write first paragraph of section 3

\documentclass[journal]{IEEEtran}
\usepackage{cite}
% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  \usepackage[pdftex]{graphicx}
%
\usepackage[cmex10]{amsmath}

@@

\section{Scattering}

>>>>

\documentclass[journal]{IEEEtran}
\usepackage{cite}
% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  \usepackage[pdftex]{graphicx}
\fi
%
\usepackage[cmex10]{amsmath}

@@

The scattering transform is a multiscale representation of audio signals which cascades an auditory filterbank and a modulation filterbank, interspersed with complex modulus nonlinearities.
The modulation filterbank may either be performed solely on the time variable or on both time and frequency.
In this section, we present the design of both the temporal scattering transform and the time-frequency scattering transform.
